---
title: "Supplementary materials"
author: "Bence Bago"
date: "14 January 2021"
output:
  rmarkdown::pdf_document:
    extra_dependencies: ["float"]
    fig_caption: yes        

header-includes: 
  \usepackage{float} \floatplacement{figure}{H} 
  \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
---

\beginsupplement
```{r setup, echo=FALSE,message=FALSE, warning=FALSE, paged.print=FALSE}
library(BayesFactor)
library(reshape2)
library(ggplot2)
library(kableExtra)

library(tidyverse)
library(jsonlite)
library(lubridate)
library(vroom)
library(countrycode)
library(gt)
library(janitor)

setwd('C:/Users/Bence/Documents/PSA-006-Trolley-problem')

trolley_raw <- vroom("data/trolley_raw.csv")

# Correct answers for attention check for the tasks
correct_answers_1 <- read_csv("meta_data/correct_answers_1.csv")
correct_answers_2 <- read_csv("meta_data/correct_answers_2.csv")

# Remove all trial runs and incomplete surveys
trolley_proc <-
  trolley_raw %>% 
  # Aggregate randomization variables
  mutate(scenario1 = case_when(FL_24_DO_Footbridgepole == 1 ~ "Pole",
                               FL_24_DO_Footbridgeswitch == 1 ~ "Switch",
                               TRUE ~ NA_character_),
         scenario2 = case_when(FL_22_DO_Standardswitch == 1 ~ "Standardswitch",
                               FL_22_DO_Standardfootbridge == 1 ~ "Standardfootbridge",
                               FL_22_DO_Loop == 1 ~ "Loop",
                               FL_22_DO_Obstaclecollide == 1 ~ "Obstaclecollide",
                               TRUE ~ NA_character_)) %>% 
  # Remove those who didn't finish the questionnaire
  filter(Progress >= 98) %>% 
  # Remove all practice runs
  filter(str_detect(str_to_lower(practice), "false")) %>% 
  # Remove the answers for a particular lab that has unflagged practice data
  filter(!(lab == "TUR_021" & StartDate < date("2020-04-22")),
         !(lab == "AUT_003" & StartDate < date("2020-06-18")),
         !(lab == "USA_095"))

# write_csv(trolley_proc, "data/trolley_preprocessed.csv")

# Exclude participants specified in the preregistration
trolley <-
  trolley_proc %>% 
  # Exclude careless responders
  filter_at(vars(careless_1, careless_2), all_vars(. != 1)) %>%
  filter(careless_3 != 2) %>%
  # Remove confused participants 
  filter(confusion != 3) %>%
  # Exclude those with familiarity of the topic
  filter(familiarity <= 3) %>%
  # Technical problems is not in the master questionnaire!
  filter(technical_problems != 2) %>% 
  # Exclude those who did not fill the questionnaire on their native language
  filter(native_language != 2)

# Remove those who can't tell which scenarios they saw
# Use the correct answer descriptions as attention check for the tasks
# Only those are kept who answered either of the tasks correctly

study1a <- 
  trolley %>%
  left_join(correct_answers_1, by = "scenario1") %>% 
  filter(trolley_attention == trolley_answer) %>%
  select(-trolley_answer, -speedboat_answer)

study1b <- 
  trolley %>% 
  left_join(correct_answers_1, by = "scenario1") %>% 
  filter(speedboat_attention == speedboat_answer) %>%
  select(-trolley_answer, -speedboat_answer)

study2a <-
  trolley %>% 
  left_join(correct_answers_2, by = "scenario2") %>% 
  filter(trolley_attention == trolley_answer) %>%
  select(-trolley_answer, -speedboat_answer)

study2b <-
  trolley %>% 
  left_join(correct_answers_2, by = "scenario2") %>% 
  filter(speedboat_attention == speedboat_answer) %>%
  select(-trolley_answer, -speedboat_answer)
```

```{r individualism score, echo=FALSE,message=FALSE, warning=FALSE, paged.print=FALSE}

cd_raw <- read_csv(here::here("data/collectivism_similarity_matrix-from_culturaldistance.com.csv"))

cd <- 
  cd_raw %>% 
  transmute(country = names(.),
            Collectivism = `United States2010-2014`) %>% 
  extract(country, 
          into = c("Country", "distance_year"), 
          regex = "(.*)(\\d{4}-\\d{4})") %>% 
  # Get the latest similarity data
  group_by(Country) %>% 
  slice_tail(n = 1) %>% 
  ungroup() %>% 
  # USA should have 0 distance (not NA)
  mutate(Collectivism = if_else(is.na(Collectivism), 0, Collectivism),
         country3 = countryname(sourcevar = Country, 
                                destination = "iso3c")) 

trolley_proc$lab=as.character(trolley_proc$lab)
trolley_proc$country3=sub("^([A-z]+)_([0-9]+)$", "\\1",  trolley_proc$lab)
levels(factor(trolley_proc$country3))
trolley_proc$country3=recode(trolley_proc$country3,SWT="CHE", LEB = "LBN", BUL = "BGR", SPA = "ESP")
trolley_proc=merge(trolley_proc, cd, by=c("country3"))



```

#1. Demographics and exclusion 

<!-- <Tamas> -->


#2. Main replication analysis

##Study 1a

###Bayesian analysis


```{r Study1a Bayesian, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

#use data study1a
survey=levels(factor(trolley_proc$survey_name))
tabledata_s1a = data.frame(Exclusion=c(rep("Exclusion",3)),Cluster=c("Eastern", "Southern", "Western"), matrix(nrow=3, ncol=5, dimnames=list(survey,c("BF","RR", "t", "df", "p"))))

for (i in survey){
dat=subset(study1a, survey_name==i, select=c("trolley_1_rate", "trolley_2_rate"))
dat_long=na.omit(melt(data=dat, variable.name = "condition", value.name="rate"))
datt=as_tibble(ttestBF(formula = rate ~ condition, data=dat_long, rscale=0.26, nullInterval = c(0, Inf)))
tabledata_s1a[i, "BF"]=signif(round(as.numeric(datt[2,1]),1),2)
frequentist=t.test(rate ~ condition, data=dat_long)
tabledata_s1a[i, "t"]=round(frequentist$statistic,2)
tabledata_s1a[i, "df"]=round(frequentist$parameter,2)
tabledata_s1a[i, "p"]=round(frequentist$p.value,4)
}

tabledata_s1a_ne = data.frame(Exclusion=c(rep("No exclusion",3)),Cluster=c("Eastern", "Southern", "Western"), matrix(nrow=3, ncol=5, dimnames=list(survey,c("BF","RR", "t", "df", "p"))))
for (i in survey){
dat=subset(trolley_proc, survey_name==i, select=c("trolley_1_rate", "trolley_2_rate"))
dat_long=na.omit(melt(data=dat, variable.name = "condition", value.name="rate"))
datt=as_tibble(ttestBF(formula = rate ~ condition, data=dat_long, rscale=0.26, nullInterval = c(0, Inf)))
tabledata_s1a_ne[i, "BF"]=signif(round(as.numeric(datt[2,1]),1),2)
frequentist=t.test(rate ~ condition, data=dat_long)
tabledata_s1a_ne[i, "t"]=round(frequentist$statistic,2)
tabledata_s1a_ne[i, "df"]=round(frequentist$parameter,2)
tabledata_s1a_ne[i, "p"]=round(frequentist$p.value,4)
}
studys1a_results = rbind(tabledata_s1a, tabledata_s1a_ne)
rownames(studys1a_results) <- NULL
studys1a_results[,"p"]<-"<.001"

studys1a_results[,"RR"]<-c("0.015, 47", "3e-08, 9e+0.6", "0.004, 14", "8e-15, 2e+13", "1e-23, 1.9e+22", "2e-19, 6e+17")

kbl(
  studys1a_results,
  format = "latex",
  booktabs = T,
  escape=T,
  caption = "Do personal force have an effect on moral dilemma judgements on Trolley dilemmas?",
  centering=T,
  position="H"
  )%>%
  kable_styling( full_width = F,  position="left")%>%
  row_spec(row=0, bold=TRUE)%>%
  collapse_rows(columns = 1, valign = "top", latex_hline = "major", row_group_label_position = "identity")

```

First, we analysed the data in which we applied all exclusion criteria regarding the trolley dilemmas. In all of the cultural clusters we investigated, we found strong evidence for the effect of personal force on moral dilemma judgements. In the Western cluster; BF = , Error = , d = ,  in the eastern cluster, BF =  and in the southern cluster too, BF = . As pre-registered we also conducted a frequentist analysis, which yielded the same conclusions. There was a significant difference in the western cluster between the personal force and no personal force conditions, t () = , p = , similarly in the southern, t () = p = , and the eastern clusters, t () = p = . Figure x. represents the results.

<!-- //Robustness analysis <PBence> -->


<!-- //graph with exclusion -->
```{r Study1a excl graph, fig.pos="H",out.width="90%",fig.cap="Results on Trolley dilemmas in Study 1 when all exclusions criteria are applied. Black points are group level averages. There is an effect of personal force on each of the three clusters.", echo =FALSE,message=FALSE, warning=FALSE, paged.print=FALSE }

full=subset(study1a, select=c("trolley_1_rate", "trolley_2_rate", "survey_name"))
full$survey_name=factor(full$survey_name)
full2=melt(data=full, variable.name = "condition", value.name="rate", id="survey_name")
full2$condition=plyr::mapvalues(full2$condition, from=c("trolley_1_rate", "trolley_2_rate"), to=c("Personal Force", "No personal force"))
full2$survey_name=plyr::mapvalues(full2$survey_name, from=c("PSA006_Eastern", "PSA006_Western", "PSA006_Southern"), to=c("Eastern", "Western", "Southern"))
full2=na.omit(full2)

source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")
lb <- function(x) mean(x, na.rm=T) - sd(x, na.rm=T)
ub <- function(x) mean(x, na.rm=T) + sd(x, na.rm=T)

sumld<- plyr::ddply(full2, ~condition+survey_name, summarise, mean = mean(rate, na.rm=T), median = median(rate, na.rm=T), lower = lb(rate), upper = ub(rate))

ggplot(full2, aes(x=condition, y=rate, fill=condition)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8)+
  geom_point(aes(y = rate, color = condition), position = position_jitter(width = .15), size = .5, alpha = 0.8) +
  stat_summary(fun=mean,geom="line", aes(group=1),position = position_nudge(x = 0.3), size = 1)+
  geom_line(data = sumld, aes(x = condition, y = mean), position = position_nudge(x = 0.3), size = 2.5)+
  geom_point(data = sumld, aes(x = condition, y = mean), position = position_nudge(x = 0.3), size = 2.5) +
  #geom_errorbar(data = sumld, aes(ymin = lower, ymax = upper, y = mean), position = position_nudge(x = 0.3), width = 0) +
  guides(fill = FALSE) +
  guides(color = FALSE) +
  facet_wrap(facets=vars(survey_name)) +
  labs( y="To what extent is this action morally acceptable?")+ theme_bw()+
  expand_limits(y=c(1,9))+scale_y_continuous(breaks=c(1,2,3,4,5,6,7,8,9))+
  theme(panel.grid.major=element_blank(),panel.grid.minor=element_blank(),plot.title=element_text( hjust=0.5, vjust=0.5, face="bold", size=17),
        axis.title.x=element_blank(), axis.title.y=element_text(face="bold", size=10), axis.text.x = element_text(face="bold", size=7, colour="Black"), axis.text.y = element_text(face="bold", size=12, colour="Black"),
        legend.title=element_blank(),legend.text=element_text(size=9))

```


<!-- //graph without exclusion -->
```{r Study1a w/o excl graph, fig.pos="H",out.width="90%",fig.cap="Results on Trolley dilemmas in Study 1 when no exclusions criteria is applied. Black points are group level averages.  There is an effect of personal force on each of the three clusters.", echo =FALSE,message=FALSE, warning=FALSE, paged.print=FALSE }

full=subset(trolley_proc, select=c("trolley_1_rate", "trolley_2_rate", "survey_name"))
full$survey_name=factor(full$survey_name)
full2=melt(data=full, variable.name = "condition", value.name="rate", id="survey_name")
full2$condition=plyr::mapvalues(full2$condition, from=c("trolley_1_rate", "trolley_2_rate"), to=c("Personal Force", "No personal force"))
full2$survey_name=plyr::mapvalues(full2$survey_name, from=c("PSA006_Eastern", "PSA006_Western", "PSA006_Southern"), to=c("Eastern", "Western", "Southern"))
full2=na.omit(full2)

source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")
lb <- function(x) mean(x, na.rm=T) - sd(x, na.rm=T)
ub <- function(x) mean(x, na.rm=T) + sd(x, na.rm=T)

sumld<- plyr::ddply(full2, ~condition+survey_name, summarise, mean = mean(rate, na.rm=T), median = median(rate, na.rm=T), lower = lb(rate), upper = ub(rate))

ggplot(full2, aes(x=condition, y=rate, fill=condition)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8)+
  geom_point(aes(y = rate, color = condition), position = position_jitter(width = .15), size = .5, alpha = 0.8) +
  stat_summary(fun=mean,geom="line", aes(group=1),position = position_nudge(x = 0.3), size = 1)+
  geom_line(data = sumld, aes(x = condition, y = mean), position = position_nudge(x = 0.3), size = 2.5)+
  geom_point(data = sumld, aes(x = condition, y = mean), position = position_nudge(x = 0.3), size = 2.5) +
  guides(fill = FALSE) +
  guides(color = FALSE) +
  facet_wrap(facets=vars(survey_name)) +
  labs( y="To what extent is this action morally acceptable?")+ theme_bw()+
  expand_limits(y=c(1,9))+scale_y_continuous(breaks=c(1,2,3,4,5,6,7,8,9))+
  theme(panel.grid.major=element_blank(),panel.grid.minor=element_blank(),plot.title=element_text( hjust=0.5, vjust=0.5, face="bold", size=17),
        axis.title.x=element_blank(), axis.title.y=element_text(face="bold", size=10), axis.text.x = element_text(face="bold", size=7, colour="Black"), axis.text.y = element_text(face="bold", size=12, colour="Black"),
        legend.title=element_blank(),legend.text=element_text(size=9))

```


##Study 1b

```{r Study1b Bayesian, echo=FALSE,message=FALSE, warning=FALSE, paged.print=FALSE}


survey=levels(factor(trolley_proc$survey_name))
tabledata_s1b = data.frame(Exclusion=c(rep("Exclusion",3)),Cluster=c("Eastern", "Southern", "Western"), matrix(nrow=3, ncol=5, dimnames=list(survey,c("BF","RR", "t", "df", "p"))))

for (i in survey){
dat=subset(study1b, survey_name==i, select=c("speedboat_1_rate", "speedboat_2_rate"))
dat_long=na.omit(melt(data=dat, variable.name = "condition", value.name="rate"))
datt=as_tibble(ttestBF(formula = rate ~ condition, data=dat_long, rscale=0.26, nullInterval = c(0, Inf)))
tabledata_s1b[i, "BF"]=signif(round(as.numeric(datt[2,1]),1),2)
frequentist=t.test(rate ~ condition, data=dat_long)
tabledata_s1b[i, "t"]=round(frequentist$statistic,2)
tabledata_s1b[i, "df"]=round(frequentist$parameter,2)
tabledata_s1b[i, "p"]=round(frequentist$p.value,3)
}

tabledata_s1b_ne = data.frame(Exclusion=c(rep("No exclusion",3)),Cluster=c("Eastern", "Southern", "Western"), matrix(nrow=3, ncol=5, dimnames=list(survey,c("BF","RR", "t", "df", "p"))))
for (i in survey){
dat=subset(trolley_proc, survey_name==i, select=c("speedboat_1_rate", "speedboat_2_rate"))
dat_long=na.omit(melt(data=dat, variable.name = "condition", value.name="rate"))
datt=as_tibble(ttestBF(formula = rate ~ condition, data=dat_long, rscale=0.26, nullInterval = c(0, Inf)))
tabledata_s1b_ne[i, "BF"]=signif(round(as.numeric(datt[2,1]),1),2)
frequentist=t.test(rate ~ condition, data=dat_long)
tabledata_s1b_ne[i, "t"]=round(frequentist$statistic,2)
tabledata_s1b_ne[i, "df"]=round(frequentist$parameter,2)
tabledata_s1b_ne[i, "p"]=round(frequentist$p.value,3)
}
studys1b_results = rbind(tabledata_s1b, tabledata_s1b_ne)
rownames(studys1b_results) <- NULL
studys1b_results[studys1b_results==0.000]<-"<.001"

kbl(
  studys1b_results,
  format = "latex",
  booktabs = T,
  escape=T,
  caption = "Do personal force have an effect on moral dilemma judgements on Speedboat dilemmas?",
  centering=T,
  position="H"
  )%>%
  kable_styling( full_width = F,  position="left")%>%
  row_spec(row=0, bold=TRUE)%>%
  collapse_rows(columns = 1, valign = "top", latex_hline = "major", row_group_label_position = "identity")
```

<!-- //Robustness analysis <PBence> -->

<!-- //graph with exclusion -->
```{r Study1b excl graph, fig.pos="H",out.width="90%",fig.cap="Results on Speedboat dilemmas in Study 1 when all exclusions criteria are applied. Black points are group level averages.  There is an effect of personal force on each of the three clusters.", echo =FALSE,message=FALSE, warning=FALSE, paged.print=FALSE }

full=subset(study1b, select=c("speedboat_1_rate", "speedboat_2_rate", "survey_name"))
full$survey_name=factor(full$survey_name)
full2=melt(data=full, variable.name = "condition", value.name="rate", id="survey_name")
full2$condition=plyr::mapvalues(full2$condition, from=c("speedboat_1_rate", "speedboat_2_rate"), to=c("Personal Force", "No personal force"))
full2$survey_name=plyr::mapvalues(full2$survey_name, from=c("PSA006_Eastern", "PSA006_Western", "PSA006_Southern"), to=c("Eastern", "Western", "Southern"))
full2=na.omit(full2)

source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")
lb <- function(x) mean(x, na.rm=T) - sd(x, na.rm=T)
ub <- function(x) mean(x, na.rm=T) + sd(x, na.rm=T)

sumld<- plyr::ddply(full2, ~condition+survey_name, summarise, mean = mean(rate, na.rm=T), median = median(rate, na.rm=T), lower = lb(rate), upper = ub(rate))

ggplot(full2, aes(x=condition, y=rate, fill=condition)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8)+
  geom_point(aes(y = rate, color = condition), position = position_jitter(width = .15), size = .5, alpha = 0.8) +
  stat_summary(fun=mean,geom="line", aes(group=1),position = position_nudge(x = 0.3), size = 1)+
  geom_line(data = sumld, aes(x = condition, y = mean), position = position_nudge(x = 0.3), size = 2.5)+
  geom_point(data = sumld, aes(x = condition, y = mean), position = position_nudge(x = 0.3), size = 2.5) +
  #geom_errorbar(data = sumld, aes(ymin = lower, ymax = upper, y = mean), position = position_nudge(x = 0.3), width = 0) +
  guides(fill = FALSE) +
  guides(color = FALSE) +
  facet_wrap(facets=vars(survey_name)) +
  labs( y="To what extent is this action morally acceptable?")+ theme_bw()+
  expand_limits(y=c(1,9))+scale_y_continuous(breaks=c(1,2,3,4,5,6,7,8,9))+
  theme(panel.grid.major=element_blank(),panel.grid.minor=element_blank(),plot.title=element_text( hjust=0.5, vjust=0.5, face="bold", size=17),
        axis.title.x=element_blank(), axis.title.y=element_text(face="bold", size=10), axis.text.x = element_text(face="bold", size=7, colour="Black"), axis.text.y = element_text(face="bold", size=12, colour="Black"),
        legend.title=element_blank(),legend.text=element_text(size=9))

```


<!-- //graph without exclusion -->
```{r Study1b w/o excl graph, fig.pos="H",out.width="90%",fig.cap="Results on Speedboat dilemmas in Study 1 when no exclusions criteria is applied. Black points are group level averages.  There is an effect of personal force on each of the three clusters.", echo =FALSE,message=FALSE, warning=FALSE, paged.print=FALSE }

full=subset(trolley_proc, select=c("speedboat_1_rate", "speedboat_2_rate", "survey_name"))
full$survey_name=factor(full$survey_name)
full2=melt(data=full, variable.name = "condition", value.name="rate", id="survey_name")
full2$condition=plyr::mapvalues(full2$condition, from=c("speedboat_1_rate", "speedboat_2_rate"), to=c("Personal Force", "No personal force"))
full2$survey_name=plyr::mapvalues(full2$survey_name, from=c("PSA006_Eastern", "PSA006_Western", "PSA006_Southern"), to=c("Eastern", "Western", "Southern"))
full2=na.omit(full2)

source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")
lb <- function(x) mean(x, na.rm=T) - sd(x, na.rm=T)
ub <- function(x) mean(x, na.rm=T) + sd(x, na.rm=T)

sumld<- plyr::ddply(full2, ~condition+survey_name, summarise, mean = mean(rate, na.rm=T), median = median(rate, na.rm=T), lower = lb(rate), upper = ub(rate))

ggplot(full2, aes(x=condition, y=rate, fill=condition)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8)+
  geom_point(aes(y = rate, color = condition), position = position_jitter(width = .15), size = .5, alpha = 0.8) +
  stat_summary(fun=mean,geom="line", aes(group=1),position = position_nudge(x = 0.3), size = 1)+
  geom_line(data = sumld, aes(x = condition, y = mean), position = position_nudge(x = 0.3), size = 2.5)+
  geom_point(data = sumld, aes(x = condition, y = mean), position = position_nudge(x = 0.3), size = 2.5) +
  #geom_errorbar(data = sumld, aes(ymin = lower, ymax = upper, y = mean), position = position_nudge(x = 0.3), width = 0) +
  guides(fill = FALSE) +
  guides(color = FALSE) +
  facet_wrap(facets=vars(survey_name)) +
  labs( y="To what extent is this action morally acceptable?")+ theme_bw()+
  expand_limits(y=c(1,9))+scale_y_continuous(breaks=c(1,2,3,4,5,6,7,8,9))+
  theme(panel.grid.major=element_blank(),panel.grid.minor=element_blank(),plot.title=element_text( hjust=0.5, vjust=0.5, face="bold", size=17),
        axis.title.x=element_blank(), axis.title.y=element_text(face="bold", size=10), axis.text.x = element_text(face="bold", size=7, colour="Black"), axis.text.y = element_text(face="bold", size=12, colour="Black"),
        legend.title=element_blank(),legend.text=element_text(size=9))

```


##Study 2a

```{r Study2a Bayesian, echo=FALSE,message=FALSE, warning=FALSE, paged.print=FALSE}

survey=levels(factor(trolley_proc$survey_name))
tabledata_s2a = data.frame(Exclusion=c(rep("Exclusion",3)),Cluster=c("Eastern", "Southern", "Western"), matrix(nrow=3, ncol=5, dimnames=list(survey,c("BF","RR", "F", "df", "p"))))

for (i in survey){
dat=subset(study2a, survey_name==i, select=c("trolley_3_rate", "trolley_4_rate", "trolley_5_rate", "trolley_6_rate"))
dat_long=na.omit(melt(data=dat, variable.name = "condition", value.name="rate"))
dat_long$personal_force = factor(ifelse(dat_long$condition=="trolley_3_rate"|dat_long$condition=="trolley_5_rate", 0, 1))
dat_long$intention = factor(ifelse(dat_long$condition=="trolley_4_rate"|dat_long$condition=="trolley_5_rate", 1, 0))
datt=lmBF(rate ~ personal_force*intention, data=dat_long, rscaleFixed=0.26)
datt2=lmBF(rate ~ personal_force+intention, data=dat_long, rscaleFixed=0.26)
datt3=as_tibble(datt/datt2)
tabledata_s2a[i, "BF"]=signif(round(datt3[1,1],1),2)
frequentist=summary(aov(rate ~ personal_force*intention, data=dat_long))[[1]]
tabledata_s2a[i, "F"]=round(frequentist[3, "F value"],3)
tabledata_s2a[i, "df"]=paste("1, ", frequentist[4, "Df"])
tabledata_s2a[i, "p"]=round(frequentist[3, "Pr(>F)"],3)
}

tabledata_s2a_ne = data.frame(Exclusion=c(rep("No exclusion",3)),Cluster=c("Eastern", "Southern", "Western"), matrix(nrow=3, ncol=5, dimnames=list(survey,c("BF","RR", "F", "df", "p"))))
for (i in survey){
dat=subset(trolley_proc, survey_name==i, select=c("trolley_3_rate", "trolley_4_rate", "trolley_5_rate", "trolley_6_rate"))
dat_long=na.omit(melt(data=dat, variable.name = "condition", value.name="rate"))
dat_long$personal_force = factor(ifelse(dat_long$condition=="trolley_3_rate"|dat_long$condition=="trolley_5_rate", 0, 1))
dat_long$intention = factor(ifelse(dat_long$condition=="trolley_4_rate"|dat_long$condition=="trolley_5_rate", 1, 0))
datt=lmBF(rate ~ personal_force*intention, data=dat_long, rscaleFixed=0.26)
datt2=lmBF(rate ~ personal_force+intention, data=dat_long, rscaleFixed=0.26)
datt3=as_tibble(datt/datt2)
tabledata_s2a_ne[i, "BF"]=signif(round(datt3[1,1],1),2)
frequentist=summary(aov(rate ~ personal_force*intention, data=dat_long))[[1]]
tabledata_s2a_ne[i, "F"]=round(frequentist[3, "F value"],3)
tabledata_s2a_ne[i, "df"]=paste("1, ", frequentist[4, "Df"])
tabledata_s2a_ne[i, "p"]=round(frequentist[3, "Pr(>F)"],3)
}
studys2a_results = rbind(tabledata_s2a, tabledata_s2a_ne)
rownames(studys2a_results) <- NULL
studys2a_results[studys2a_results==0.000]<-"<.001"

kbl(
  studys2a_results,
  format = "latex",
  booktabs = T,
  escape=T,
  caption = "Do personal force interact with intention on Trolley dilemmas?",
  centering=T,
  position="H"
  )%>%
  kable_styling( full_width = F,  position="left")%>%
  row_spec(row=0, bold=TRUE)%>%
  collapse_rows(columns = 1, valign = "top", latex_hline = "major", row_group_label_position = "identity")

```


<!-- //Robustness analysis <PBence> -->

<!-- //graph with exclusion -->
```{r Study2a excl graph,fig.pos="H",out.width="90%",fig.cap="Results on Trolley dilemmas in Study 2 when all exclusions criteria are applied. Error bars are 95\\% confidence intervals on the mean. We can observe a significant interaction between personal force and intention on all cultural clusters.", echo =FALSE,message=FALSE, warning=FALSE, paged.print=FALSE }

full=subset(study2a, select=c("trolley_3_rate", "trolley_4_rate", "trolley_5_rate", "trolley_6_rate", "survey_name"))
full$survey_name=factor(full$survey_name)
full2=melt(data=full, variable.name = "condition", value.name="rate", id="survey_name")
full2$personal_force=plyr::mapvalues(full2$condition, from=c("trolley_3_rate", "trolley_4_rate", "trolley_5_rate", "trolley_6_rate"), to=c("No Personal Force", "Personal force", "No Personal Force", "Personal force"))
full2$intention=plyr::mapvalues(full2$condition, from=c("trolley_3_rate", "trolley_4_rate", "trolley_5_rate", "trolley_6_rate"), to=c("No Intention", "Intention", "Intention", "No Intention"))

full2$survey_name=plyr::mapvalues(full2$survey_name, from=c("PSA006_Eastern", "PSA006_Western", "PSA006_Southern"), to=c("Eastern", "Western", "Southern"))
full2=na.omit(full2)



ggplot(full2, aes(x=intention, y=rate, fill=personal_force, width=0.7)) +
  stat_summary(fun=mean, geom="bar", position="dodge", colour="Black",  width=1.2)+
  stat_summary(fun.data=mean_cl_boot, geom="errorbar", position=position_dodge(width=0.7), colour="Black", width=0.2)+
  facet_wrap(facets=vars(survey_name)) +
  labs( y="To what extent is this action morally acceptable?")+ theme_bw()+
  expand_limits(y=c(1,9))+scale_y_continuous(breaks=c(1,2,3,4,5,6,7,8,9))+
  theme(panel.grid.major=element_blank(),panel.grid.minor=element_blank(),plot.title=element_text( hjust=0.5, vjust=0.5, face="bold", size=17),
        axis.title.x=element_blank(), axis.title.y=element_text(face="bold", size=10), axis.text.x = element_text(face="bold", size=7, colour="Black"), axis.text.y = element_text(face="bold", size=12, colour="Black"),
        legend.title=element_blank(),legend.text=element_text(size=9))

```


<!-- //graph without exclusion -->
```{r Study2a w/o excl graph, fig.pos="H",out.width="90%",fig.cap="Results on Trolley dilemmas in Study 2 when no exclusion criteria are applied. Error bars are 95\\% confidence intervals on the mean. We can observe a significant interaction between personal force and intention on all cultural clusters.",  echo =FALSE,message=FALSE, warning=FALSE, paged.print=FALSE }

full=subset(trolley_proc, select=c("trolley_3_rate", "trolley_4_rate", "trolley_5_rate", "trolley_6_rate", "survey_name"))
full$survey_name=factor(full$survey_name)
full2=melt(data=full, variable.name = "condition", value.name="rate", id="survey_name")
full2$personal_force=plyr::mapvalues(full2$condition, from=c("trolley_3_rate", "trolley_4_rate", "trolley_5_rate", "trolley_6_rate"), to=c("No Personal Force", "Personal force", "No Personal Force", "Personal force"))
full2$intention=plyr::mapvalues(full2$condition, from=c("trolley_3_rate", "trolley_4_rate", "trolley_5_rate", "trolley_6_rate"), to=c("No Intention", "Intention", "Intention", "No Intention"))

full2$survey_name=plyr::mapvalues(full2$survey_name, from=c("PSA006_Eastern", "PSA006_Western", "PSA006_Southern"), to=c("Eastern", "Western", "Southern"))
full2=na.omit(full2)



ggplot(full2, aes(x=intention, y=rate, fill=personal_force, width=0.7)) +
  stat_summary(fun=mean, geom="bar", position="dodge", colour="Black",  width=1.2)+
  stat_summary(fun.data=mean_cl_boot, geom="errorbar", position=position_dodge(width=0.7), colour="Black", width=0.2)+
  facet_wrap(facets=vars(survey_name)) +
  labs( y="To what extent is this action morally acceptable?")+ theme_bw()+
  expand_limits(y=c(1,9))+scale_y_continuous(breaks=c(1,2,3,4,5,6,7,8,9))+
  theme(panel.grid.major=element_blank(),panel.grid.minor=element_blank(),plot.title=element_text( hjust=0.5, vjust=0.5, face="bold", size=17),
        axis.title.x=element_blank(), axis.title.y=element_text(face="bold", size=10), axis.text.x = element_text(face="bold", size=7, colour="Black"), axis.text.y = element_text(face="bold", size=12, colour="Black"),
        legend.title=element_blank(),legend.text=element_text(size=9))

```


##Study 2b

```{r study2b Bayesian, echo=FALSE,message=FALSE, warning=FALSE, paged.print=FALSE}
survey=levels(factor(trolley_proc$survey_name))
tabledata_s2b = data.frame(Exclusion=c(rep("Exclusion",3)),Cluster=c("Eastern", "Southern", "Western"), matrix(nrow=3, ncol=5, dimnames=list(survey,c("BF","RR", "F", "df", "p"))))

for (i in survey){
dat=subset(study2b, survey_name==i, select=c("speedboat_3_rate", "speedboat_4_rate", "speedboat_5_rate", "speedboat_6_rate"))
dat_long=na.omit(melt(data=dat, variable.name = "condition", value.name="rate"))
dat_long$personal_force = factor(ifelse(dat_long$condition=="speedboat_3_rate"|dat_long$condition=="speedboat_5_rate", 0, 1))
dat_long$intention = factor(ifelse(dat_long$condition=="speedboat_4_rate"|dat_long$condition=="speedboat_5_rate", 1, 0))
datt=lmBF(rate ~ personal_force*intention, data=dat_long, rscaleFixed=0.26)
datt2=lmBF(rate ~ personal_force+intention, data=dat_long, rscaleFixed=0.26)
datt3=as_tibble(datt/datt2)
tabledata_s2b[i, "BF"]=signif(round(datt3[1,1],1),2)
frequentist=summary(aov(rate ~ personal_force*intention, data=dat_long))[[1]]
tabledata_s2b[i, "F"]=round(frequentist[3, "F value"],3)
tabledata_s2b[i, "df"]=paste("1, ", frequentist[4, "Df"])
tabledata_s2b[i, "p"]=round(frequentist[3, "Pr(>F)"],3)
}

tabledata_s2b_ne = data.frame(Exclusion=c(rep("No exclusion",3)),Cluster=c("Eastern", "Southern", "Western"), matrix(nrow=3, ncol=5, dimnames=list(survey,c("BF","RR", "F", "df", "p"))))
for (i in survey){
dat=subset(trolley_proc, survey_name==i, select=c("speedboat_3_rate", "speedboat_4_rate", "speedboat_5_rate", "speedboat_6_rate"))
dat_long=na.omit(melt(data=dat, variable.name = "condition", value.name="rate"))
dat_long$personal_force = factor(ifelse(dat_long$condition=="speedboat_3_rate"|dat_long$condition=="speedboat_5_rate", 0, 1))
dat_long$intention = factor(ifelse(dat_long$condition=="speedboat_4_rate"|dat_long$condition=="speedboat_5_rate", 1, 0))
datt=lmBF(rate ~ personal_force*intention, data=dat_long, rscaleFixed=0.26)
datt2=lmBF(rate ~ personal_force+intention, data=dat_long, rscaleFixed=0.26)
datt3=as_tibble(datt/datt2)
tabledata_s2b_ne[i, "BF"]=signif(round(datt3[1,1],1),2)
frequentist=summary(aov(rate ~ personal_force*intention, data=dat_long))[[1]]
tabledata_s2b_ne[i, "F"]=round(frequentist[3, "F value"],3)
tabledata_s2b_ne[i, "df"]=paste("1, ", frequentist[4, "Df"])
tabledata_s2b_ne[i, "p"]=round(frequentist[3, "Pr(>F)"],3)
}
studys2b_results = rbind(tabledata_s2b, tabledata_s2b_ne)
rownames(studys2b_results) <- NULL
studys2b_results[studys2b_results==0.000]<-"<.001"

kbl(
  studys2b_results,
  format = "latex",
  booktabs = T,
  escape=T,
  caption = "Do personal force interact with intention on Speedboat dilemmas?",
  centering=T,
  position="H"
  )%>%
  kable_styling( full_width = F,  position="left")%>%
  row_spec(row=0, bold=TRUE)%>%
  collapse_rows(columns = 1, valign = "top", latex_hline = "major", row_group_label_position = "identity")



```

<!-- //Robustness analysis <PBence> -->

<!-- //graph with exclusion -->
```{r study2b excl graph, fig.pos="H",out.width="90%",fig.cap="Results on the Speedboat dilemmas in Study 2 when all exclusion criteria are applied. Error bars are 95\\% confidence intervals on the mean. We can observe a significant interaction between personal force and intention only on the Western cluster.",  echo =FALSE,message=FALSE, warning=FALSE, paged.print=FALSE }

full=subset(study2b, select=c("speedboat_3_rate", "speedboat_4_rate", "speedboat_5_rate", "speedboat_6_rate", "survey_name"))
full$survey_name=factor(full$survey_name)
full2=melt(data=full, variable.name = "condition", value.name="rate", id="survey_name")
full2$personal_force=plyr::mapvalues(full2$condition, from=c("speedboat_3_rate", "speedboat_4_rate", "speedboat_5_rate", "speedboat_6_rate"), to=c("No Personal Force", "Personal force", "No Personal Force", "Personal force"))
full2$intention=plyr::mapvalues(full2$condition, from=c("speedboat_3_rate", "speedboat_4_rate", "speedboat_5_rate", "speedboat_6_rate"), to=c("No Intention", "Intention", "Intention", "No Intention"))

full2$survey_name=plyr::mapvalues(full2$survey_name, from=c("PSA006_Eastern", "PSA006_Western", "PSA006_Southern"), to=c("Eastern", "Western", "Southern"))
full2=na.omit(full2)



ggplot(full2, aes(x=intention, y=rate, fill=personal_force, width=0.7)) +
  stat_summary(fun=mean, geom="bar", position="dodge", colour="Black",  width=1.2)+
  stat_summary(fun.data=mean_cl_boot, geom="errorbar", position=position_dodge(width=0.7), colour="Black", width=0.2)+
  facet_wrap(facets=vars(survey_name)) +
  labs( y="To what extent is this action morally acceptable?")+ theme_bw()+
  expand_limits(y=c(1,9))+scale_y_continuous(breaks=c(1,2,3,4,5,6,7,8,9))+
  theme(panel.grid.major=element_blank(),panel.grid.minor=element_blank(),plot.title=element_text( hjust=0.5, vjust=0.5, face="bold", size=17),
        axis.title.x=element_blank(), axis.title.y=element_text(face="bold", size=10), axis.text.x = element_text(face="bold", size=7, colour="Black"), axis.text.y = element_text(face="bold", size=12, colour="Black"),
        legend.title=element_blank(),legend.text=element_text(size=9))

```


<!-- //graph without exclusion -->
```{r study2b w/o excl graph,fig.pos="H",out.width="90%",fig.cap="Results on the Speedboat dilemmas in Study 2 when no exclusion criteria is applied. Error bars are 95\\% confidence intervals on the mean. We can observe a significant interaction between personal force and intention only on the Western cluster.", echo =FALSE,message=FALSE, warning=FALSE, paged.print=FALSE }

full=subset(trolley_proc, select=c("speedboat_3_rate", "speedboat_4_rate", "speedboat_5_rate", "speedboat_6_rate", "survey_name"))
full$survey_name=factor(full$survey_name)
full2=melt(data=full, variable.name = "condition", value.name="rate", id="survey_name")
full2$personal_force=plyr::mapvalues(full2$condition, from=c("speedboat_3_rate", "speedboat_4_rate", "speedboat_5_rate", "speedboat_6_rate"), to=c("No Personal Force", "Personal force", "No Personal Force", "Personal force"))
full2$intention=plyr::mapvalues(full2$condition, from=c("speedboat_3_rate", "speedboat_4_rate", "speedboat_5_rate", "speedboat_6_rate"), to=c("No Intention", "Intention", "Intention", "No Intention"))

full2$survey_name=plyr::mapvalues(full2$survey_name, from=c("PSA006_Eastern", "PSA006_Western", "PSA006_Southern"), to=c("Eastern", "Western", "Southern"))
full2=na.omit(full2)



ggplot(full2, aes(x=intention, y=rate, fill=personal_force, width=0.7)) +
  stat_summary(fun=mean, geom="bar", position="dodge", colour="Black",  width=1.2)+
  stat_summary(fun.data=mean_cl_boot, geom="errorbar", position=position_dodge(width=0.7), colour="Black", width=0.2)+
  facet_wrap(facets=vars(survey_name)) +
  labs( y="To what extent is this action morally acceptable?")+ theme_bw()+
  expand_limits(y=c(1,9))+scale_y_continuous(breaks=c(1,2,3,4,5,6,7,8,9))+
  theme(panel.grid.major=element_blank(),panel.grid.minor=element_blank(),plot.title=element_text( hjust=0.5, vjust=0.5, face="bold", size=17),
        axis.title.x=element_blank(), axis.title.y=element_text(face="bold", size=10), axis.text.x = element_text(face="bold", size=7, colour="Black"), axis.text.y = element_text(face="bold", size=12, colour="Black"),
        legend.title=element_blank(),legend.text=element_text(size=9))

```


#3. Individualism-collectivism

##Study 1a

<!-- Bayesian country level individualism w/o exclusion <MARCI> -->

<!-- Bayesian personal level individualism  w/o exclusion <MARCI>-->

```{r study1a overall individualism plot, fig.pos="H",out.width="90%",fig.cap="Correlation between country-level individualism/collectivism and the effect of personal force in Cohan D on the Trolley dilemmas", echo =FALSE,message=FALSE, warning=FALSE, paged.print=FALSE}
##cohen d calculation for every country
#scatterplot: x effect size, y individualism
#size of dots: cohen d
countrydata=data.frame(country=levels(factor(trolley_proc$country3)), matrix(nrow=length(levels(factor(trolley_proc$country3))),ncol=3, dimnames=list(levels(factor(trolley_proc$country3)), c("cohend","Collectivism","N") )))

for (i in levels(factor(trolley_proc$country3))){
  d=subset(trolley_proc, country3==i, select=c("trolley_1_rate", "trolley_2_rate"))
  dat_long=na.omit(melt(data=d, variable.name = "condition", value.name="rate"))
  countrydata[i,"cohend"]=effsize::cohen.d(rate~condition, data=dat_long)$estimate
  countrydata[i,"Collectivism"]=mean(trolley_proc[trolley_proc$country3==i,]$Collectivism, na.rm=T)
  countrydata[i,"N"]=length(dat_long$rate)
}
countrydata=na.omit(countrydata)
ggplot(countrydata, aes(x=cohend, y=Collectivism, label=country)) +
  geom_point(aes(size=N))+
  geom_text(hjust=-0.2,size=3)+
  geom_smooth(method=lm, se=F)+ 
  xlab("Effect size")+
  theme_bw()+
  theme(panel.grid.major=element_blank(),panel.grid.minor=element_blank(),plot.title=element_text( hjust=0.5, vjust=0.5, face="bold", size=17),
        axis.title.x=element_text(face="bold", size=12, colour="Black"), axis.title.y=element_text(face="bold", size=12, colour="Black"), axis.text.x = element_text(face="bold", size=10, colour="Black"), axis.text.y = element_text(face="bold", size=12, colour="Black"),
        legend.title=element_text(face="bold", size=10, colour="Black"),legend.text=element_text(size=9))
  
  

```

##Study 1b

<!-- Bayesian country level individualism w/o exclusion<MARCI> -->

<!-- Bayesian personal level individualism  w/o exclusion<MARCI>-->


##Study 2a

<!-- Bayesian country level individualism w/o exclusion<MARCI> -->

<!-- Bayesian personal level individualism  w/o exclusion<MARCI>-->

##Study 2b

<!-- Bayesian country level individualism w/o exclusion<MARCI> -->

<!-- Bayesian personal level individualism  w/o exclusion<MARCI>-->


<!-- scatterplot visualisation  <BBENCE>-->

#4. Additional analysis

<!-- Oxford Utilitarianism Scale <PBENCE> -->

<!-- effect of physical contact and intention separately for speedboat (study 1b and 2b) and trolley dilemmas Bayesian analysis pre-defined priors <BBence> -->



